Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
revise section III

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. Also, we resort to the use of support vector machines (SVMs) with default parameters ($C=1$) for computing classification accuracy for the ASC task, as SVMs are widely used in the community and allows us to better root our work and focus our performance analysis on the earlier processing stages. Moreover, since the MFCCs are well established features and perform well in this task, they will be thoroughly used as baselines features in the experiments described in this paper.

@@

For most of the experiments reported in this paper, the DCASE2013 datatset is considered \cite{giannoulis2013database, 7100934}. To build this dataset, three different recordists visited a wide variety of locations in Greater London over
a period of months and in each
scene recorded a few minutes of audio for each scene type. No
systematic variations in the recordings covaried with scene
type: all recordings were made in moderate weather condi-
tions, and varying times of day and week, and each recordist
recorded each scene type. The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a 5 fold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.

As of today, there exist larger publicly available dataset, the
Rouen dataset \cite{rakotomamonjy2015histogram} and the dCase2016 \cite{Mesaros2016_EUSIPCO} (only the public part). The latter is also considered in this paper as a validation of the proposed approach.

As studied in \cite{lagrange:hal-01082501}, the DCASE2013 dataset has interesting intra class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices. Also, it is still challenging as state-of-the-art systems based on features design and support vector machines (SVMs) achieves 76 \% \cite{roma2013} (winner of the 2013 challenge RQA+SVM). For the sake of comparison the HOG+SVM approach \cite{rakotomamonjy2015histogram} achieves 75 \% and 92 \% on the dcase2013 and the Rouen datasets respectively. On the former, recent advances using hierarchical classifiers architectures reports 84 to 87 \% of accuracy depending on the prior knowledge considered for building the classifier architecture \cite{phan2016label}. On the latter, the state-of-the-art is currently 95 \% \cite{bisot2016acoustic}.

>>>>

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. Also, we resort to the use of support vector machines (SVMs) with default parameters ($C=1$) for computing classification accuracy for the ASC task, as SVMs are widely used in the community and allows us to better root our work and focus our performance analysis on the earlier processing stages. Moreover, since MFCCs are well established features and perform well in this task, they will be thoroughly used as baselines features in the experiments described in this paper.

@@

Most of the experiments reported in this paper rely on the DCASE2013 \cite{giannoulis2013database, 7100934}. To build this dataset, three different recordists visited a wide variety of locations in Greater London over
a period of months and in each
scene recorded a few minutes of audio for each scene type. No
systematic variations in the recordings covaried with scene
type: all recordings were made in moderate weather conditions, and varying times of day and week, and each recordist
recorded each scene type. The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a $5$-fold cross validation scheme. The folds used throughout this paper are the same as the ones used during the challenge.

As of today, there exist some larger publicly available datasets, namely the
Rouen dataset \cite{rakotomamonjy2015histogram} and the public part of dCase2016 \cite{Mesaros2016_EUSIPCO}. The latter is also considered in this paper as a validation of the proposed approach.

As studied in \cite{lagrange:hal-01082501}, the DCASE2013 dataset has interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices.
Moreover, is still highly challenging, because state-of-the-art systems based on feature design and support vector machines (SVMs) achieve 76 \% \cite{roma2013} (winner of the 2013 challenge RQA+SVM). For the sake of comparison, the HOG+SVM approach \cite{rakotomamonjy2015histogram} achieves an accuracy of 75 \% on DCASE 2013 while topping at 92 \% on the Rouen dataset.
On the former, recent advances using hierarchical classifiers architectures reports 84 to 87 \% of accuracy depending on the prior knowledge considered for building the classifier architecture \cite{phan2016label}.
On the latter, the state-of-the-art is currently 95 \% \cite{bisot2016acoustic}.
